\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-06-22 redaction/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
1eres modifs dans texte (IV)

Therefore, we propose to compare our main estimates with those stemming from a two-stage least-squares procedure. Put differently, we replace in the right-hand side of Equation (\ref{eq:model_IetA}) $\widetilde{p}$ by predicted values stemming from a first-stage equation regressing $\widetilde{p}$  on custom duties coming based on tariffs at the product line, together with one-year lagged fas prices. Section \ref{app:first_stage_IV} in Appendix \ref{app:more_results} provides a full presentation of the theoretical basis for the first-stage equation, as well as first-stage estimates. In particular, it shows that our main Instrumental Variable displays the right statistical properties, ant that we can confidently re-inject the predictions arising from the first-stage equation for $\widetilde{p}_{ik}$ on the right-hand side of Equation (\ref{eq:model_IetA}\footnote{Note that, since the predictions are expressed in logarithms, they are transformed through the exponential function before their implementation in Equation (\ref{eq:model_IetA}.} to produce a 2SLS-type of estimation. Figure \ref{fig:comp_IV_SITC5} below reports our benchmark estimates by transport mode, together with their instrumented counterpart. In all cases, these estimates are very similar, when not identical. This supports that our benchmark estimates do not suffer any substantial biases arising from endogeneity concerns.

@@

Our main instrumental variable for the fas price $\widetilde{p}_{ikt}$ is the share of tariff duties over the total value imported, at the product line. Tariffs may be considered as a (reasonably) exogenous source of variation for fas prices, i.e., uncorrelated with transport costs changes and mostly independent from firm- or sector-level dynamics. In this respect, considering the predicted part of the fas price related to tariff duties is likely to solve potential endogeneity biases. In other words, tariff shocks should eliminate from the fas price any endogenous component that might me related to transport costs.

@@

Note that in such a formulation, $\log \widetilde{p}_{ikt-1}$ appears as a second excluded instrument for $\log \widetilde{p}_{ikt}$. The $\alpha$ parameter should fall between $-1$ and $0$, and has a direct theoretical interpretation in terms of ``pricing-to-market'' behavior of firms. $\alpha = 0$ corresponds to the case where the considered sector is made of firms not adjusting their fas price to the change in tariff, that would cancel out the influence of the tariff change on the price paid by the US consumers; this rather corresponds to small firms which do not have enough market power to manipulate their prices following changes in international competition. $\alpha = -1$ is the other polar case: the sector here displays full pricing-to-market, because it involves large firms fully compensating the tariff change through their margin (see \citealp{Berman_Martin_Mayer_2012}).
In-between, $\alpha$ $\in$ $]-1,0[$ corresponds to some variable degree of``pricing-to-market'' in the sector, characterized by firms offsetting partly the impact of the tariff change on the fas price by adjusting the producer price in the opposite direction of the tariff change.

@@

Table \ref{tab: FS_sitc5} suggests that custom duties variations are a satisfactory predictor of fas prices $\widetilde{p}_{ik}$, with strong significance. The F-statistic on the excluded instrument ($\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d}$ ($\widehat{\alpha}$)) is on average above 10, the ``rule-of-thumb'' threshold value recommended by \cite{staiger_stock} as a test for weak instrumentation. In addition, Figure \ref{fig: FS_IV_SITC5} shows that most values of the $\alpha$ parameter stand between 0 and -1, as expected, except in 3 or 4 occasions, corresponding to abrupt fluctuations in oil prices. This is typically the case in 1975, with $\alpha$=-1.83. All in all, these estimates make us confident in the validity of our instrumentation strategy.

@@

Results are qualitatively very similar to those reported on the longer-time-span, more-aggregated-SITC5 dataset previously reported. The F-statistic on the excluded instrument ($\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d}$ ($\widehat{\alpha}$)) is on average close to 12, slightly higher than in our benchmark. As previously, Figure \ref{fig: FS_IV_HS10} shows that most values of the $\alpha$ parameter stand between 0 and -1, as expected, except in a few years which seem again to coincide with significant fluctuations in oil prices - e.g. Interestingly, the value of the $\alpha$ parameter is on average -0.36, lower than in our benchmark on SITC5 data. At this highly disaggregated level, pricing-to-market behavior seems less strong, indicating that the average firm is smaller than its average SITC5 counterpart. Interestingly, this average value is almost identical to the one found by \citet{Fontagne_Martin_Orefice2018} on French HS6 data between 1995 and 2010 (see the first-stage coefficients in their Table 6), or by \citet{Bussiere2013} on country-level data between 1980 and 2006. In any case, this strengthens our confidence in the validity of our estimation strategy.

>>>>

Therefore, we propose to compare our main estimates with those stemming from a two-stage least-squares procedure. Put differently, we follow earlier literature (see e.g. \citealp{Caliendo_Parro_2015} or \citealp{Lashkaripour-2017}) by replacing in the right-hand side of Equation (\ref{eq:model_IetA}) $\widetilde{p}$ by predicted values stemming from a first-stage equation regressing $\widetilde{p}$  on custom duties coming based on tariffs at the product line, together with one-year lagged fas prices. Section \ref{app:first_stage_IV} in Appendix \ref{app:more_results} provides a full presentation of the theoretical basis for the first-stage equation, as well as first-stage estimates. In particular, it shows that our main instrumental variable displays the right statistical properties, and that we can confidently re-inject the predictions arising from the first-stage equation for $\widetilde{p}_{ik}$ on the right-hand side of Equation (\ref{eq:model_IetA}\footnote{Note that, since the predictions are expressed in logarithms, they are transformed through the exponential function before their implementation in Equation (\ref{eq:model_IetA}.} to produce a 2SLS-type of estimation. Figure \ref{fig:comp_IV_SITC5} below reports our benchmark estimates by transport mode, together with their instrumented counterpart. In all cases, these estimates are very similar, when not identical. This supports that our benchmark estimates do not suffer any substantial biases arising from endogeneity concerns.

@@

Our main instrumental variable for the fas price $\widetilde{p}_{ikt}$ is the share of tariff duties over the total value imported, at the product line. Tariffs may be considered as a (reasonably) exogenous source of variation for fas prices, i.e., uncorrelated with transport costs changes and mostly independent from firm- or sector-level dynamics. In this respect, considering the predicted part of the fas price related to tariff duties is likely to solve potential endogeneity biases. In other words, tariff shocks should eliminate from the fas price any endogenous component that might be related to transport costs. Note that this strategy has been regularly used in the related literature - see for example \citet{Caliendo_Parro_2015} or \citet{Lashkaripour-2017}.

@@

Note that in such a formulation, $\log \widetilde{p}_{ikt-1}$ appears as a second instrument for $\log \widetilde{p}_{ikt}$. The $\alpha$ parameter should fall between $-1$ and $0$, and has a direct theoretical interpretation in terms of ``pricing-to-market'' behavior of firms. $\alpha = 0$ corresponds to the case where the considered sector is made of firms not adjusting their fas price to the change in tariff, that would cancel out the influence of the tariff change on the price paid by the US consumers; this rather corresponds to small firms which do not have enough market power to manipulate their prices following changes in international competition. $\alpha = -1$ is the other polar case: the sector here displays full pricing-to-market, because it involves large firms fully compensating the tariff change through their margin (see \citealp{Berman_Martin_Mayer_2012}).
In-between, $\alpha$ $\in$ $]-1,0[$ corresponds to some variable degree of``pricing-to-market'' in the sector, characterized by firms offsetting partly the impact of the tariff change on the fas price by adjusting the producer price in the opposite direction of the tariff change.

@@

Table \ref{tab: FS_sitc5} suggests that custom duties variations are a satisfactory predictor of fas prices $\widetilde{p}_{ik}$, with strong significance and the correct, negative sign. The lagged fas price $\log \widetilde{p}_{ikt-1}$ displays also the expected positive sign: with a $\beta$ parameter around 0.75 on average, fas prices exhibit substantial persistence. The F-statistic on the excluded instrument ($\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d}$ ($\widehat{\alpha}$)) is on average above 10, the ``rule-of-thumb'' threshold value recommended by \cite{staiger_stock} as a test for weak instrumentation. In addition, Figure \ref{fig: FS_IV_SITC5} shows that most values of the $\alpha$ parameter stand between 0 and -1, as expected, except in a very small number of occasions, corresponding to abrupt fluctuations in oil prices. This is typically the case in 1975, with $\alpha$=-1.83. All in all, these estimates make us confident in the validity of our instrumentation strategy.

@@

Results are qualitatively very similar to those reported on the longer-time-span, more-aggregated-SITC5 dataset previously reported. The F-statistic on the excluded instrument ($\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d}$ ($\widehat{\alpha}$)) is on average close to 12, slightly higher than in our benchmark. As previously, Figure \ref{fig: FS_IV_HS10} shows that most values of the $\alpha$ parameter stand between 0 and -1, as expected, except in a few years which seem again to coincide with significant fluctuations in oil prices. Interestingly, the value of the $\alpha$ parameter is on average -0.36, lower than in our benchmark on SITC5 data. At this highly disaggregated level, pricing-to-market behavior seems less strong, indicating that the average firm is smaller than its average SITC5 counterpart. In addition, this average value is almost identical to the one found by \citet{Fontagne_Martin_Orefice2018} on French HS6 data between 1995 and 2010 (see the first-stage coefficients in their Table 6), or by \citet{Bussiere2013} on country-level data between 1980 and 2006. In any case, this strengthens our confidence in the validity of our estimation strategy.
